Missing data: Current practice in football research and recommendations for improvement

### 2020-09-10 paper/paper.Rmd
edit data for missing data figure in the paper.

# Aim of this section:
# Simulate data from a real data set, insert missing
# 'Study aim': predicting super coach scores

@@

data <-
  d %>% select(
    ID,
    Round,
    First.name,
    Surname,
    Kicks,
    Handballs,
    Marks,
    Hit.Outs,
    Contested.Possessions,
    Uncontested.Possessions
  )

@@

# Generate the y-variable
df <- get_footywire_stats(10286:10290) # Get the fantasy scores
fit <- lm(AF ~ K + HB, data = df)
summary(fit)
data %>% mutate(fanasty_score = 4.106*Kicks + 2.175*Handballs) # Need to work on this line

# Put the dataset together
# Impute missing values
data <- ampute(data = df[,10:43])
data <- df_first_try$amp

>>>>

# Aim of this section:
# Simulate data from a real data set, insert missing
# 'Study aim': predicting hamstring strain injury, using number of sprints and sprint distance as x-variables
# Add a sentence in the paper talking about this
# I'm stuck at the momement how to simulate the occurance of an injury (0,1), but with only low incidence of 1's in the dataset
# I'm also stuck how to simulate the number of sprints, but between say 50 and 200 sprints

@@

data <-
  d %>% select(
    ID,
    Round,
    First.name,
    Surname
    )

@@

# Simulate number of sprints per game
Observations = nrow(data)
sprints <- sample.int(100, # numbers of sprints between 1 and 100
           nrow(data),
           replace = T) # observations

# Simulate incidence of hamstring strain injuries
# sample.int(100, # numbers of sprints between 1 and 100
#            nrow(data),
#            replace = T) # observations

data <- merge(data, sprints)

# Impute missing values
data <- ampute(data = df[,10:43])
data <- df_first_try$amp

# Put the dataset together
# Impute missing values
data <- ampute(data = df[,10:43])
data <- data$amp
